Modular Metatheory for Abstract Interpreters

### 2014-11-07 writeup/pldi15.tex
some sed preprocessing for -- comments.  also cleaned up what make does
monadic interpreter and fixes to makeg
added matt's abstract

% Abstract {-{
% \begin{abstract}
% \end{abstract}
% }-}

\input{pldi15.autogen.tex}

>>>>

Abstract {-{
\begin{abstract}

The design and implementation of static analyzers have becoming increasingly systematic.
In fact, design and implementation have remained seemingly on the verge of full mechanization for several years.
A stumbling block in full mechanization has been the ad hoc nature of soundness proofs accompanying each analyzer.
While design and implementation is largely systematic, 
  soundness proofs can change significantly with (apparently) minor changes to the semantics and analyzers themselves.
We finally reconcile the systematic construction of static analyzers with their proofs of soundness 
  via a mechanistic Galois-connection-based metatheory for static analyzers.

\end{abstract}
}-}

\input{tmp/autogen/pldi15.markdown.tex}
